\vspace{-3em} \includegraphics[width=.1\textwidth]{Figures/logo.png} \\ \includegraphics[width=4cm]{Figures/logotext.png} \\

### 2014-11-07 report/sdc_report.tex
final report tweaks

%----------------------------------------------------------------------------------------
%	ABSTRACT
%----------------------------------------------------------------------------------------
\vspace{-4em}
\section*{Overview}

@@

I analysed the {\bf London house prices} dataset in several creative
ways. Firstly, the \emph{fractal context} of an area visualises how house
prices relate to those of neighbouring areas at different scales up
and down the postcode hierarchy. Secondly, I fit \emph{ARIMA models}
to forecast an area's price trend into the future, with an eye to
suggesting profitable investments. Finally, growth and other metrics
were combined into an \emph{investment grade} for a given postcode
area. Together this set of analyses forms the basis of \logo, a
startup aimed at \emph{democratising real estate investment}, offering
individuals and businesses quantitative property area insights to
enable data-driven investment decisions.

@@

Letting and sales sites sometimes list some recent sales in a given
area, but it's not currently possible to get a quantitative overview
of property prices in a region, within the context of its sector,
district and postcode.

@@

These questions can be answered with a clear and intuitive data
visualisation of price distributions in the postcode hierarchy --- what
I've called the fractal context of a property price (Figure 1).

Any chosen area can be seen in the context of its surroundings, from
full postcodes to much wider areas, clearly showing how the pricing of
any given property relates to those nearby.  The example graphic for
postcode SW18 4HU (Figure 1) combines ranked violin density plots and
a geo-heatmap for a clear, intuitive view of a location's price
context.

@@

Property investors need a method of evaluating the potential investment
returns of a given property area. This can be achieved through time
series modelling with autoregressive integrated moving average (ARIMA)
models (Figure 2). For this application regularised models were fit
which allowed a $drift$ term to capture non-stationary trends
(i.e. allowing for gain, loss or neither) as well as coefficients
reflecting periodicity or seasonal effects. Hence potential investment
returns could then be optimised by selecting areas with
maximal growth projections.

\begin{figure}[h]
\begin{center}
\includegraphics[width=.9\textwidth]{Figures/arima.png}
\caption{Example ARIMA forecast of median house prices for a specific postcode.}
\end{center}
\end{figure}

\vspace{-2em}
\subsection*{Investment grading}

Combining growth forecasts and with an additional measure of
variability allows an approximate investment grading of each sector,
relative to other postcodes within the area covered by this
dataset. This intuitive output metric can help prioritise areas ripe
for property investment and combines the theoretical model projections
with an empirical metric of past stability.

@@

There are currently no mainsteam property sales or rental sites that
attempt to provide any quantitative insights that contextualise a
property's list price. Some list recent nearby sales in plain text,
but the wealth of historical sales data available allows for much
richer displays (as demonstrated with the fractal context view,
Section A: Figure 1, and by the interactive data-driven map shown in
Figure 5), which offer valuable and practical insights to prospective
homebuyers.

@@

\logo \hspace{.1em} will release an initial product both as a {\bf web
  service} and associated {\bf mobiles and tablet applications}
(Figure 6). These
offer limited analysis and visualisation without any fee, with
collected user data and feedback helping to validate the business
model and futher develop our software.

@@

Releasing these products aligns with our aims of democratising real
estate investment. Amateur property investors and prospective
landlords can make data-driven decisions, the likes of which are 
already employed by analysts for large investment funds.

A small data science team will gradually expand the range of analyses
offered, integrating novel public and privately-acquired datasets and
release them to a premium app under a rolling subscription model,
aimed at private landlords and property speculators as well as
professional real estate investment trusts (REITs). Significant
revenue could be generated through tailored partnerships with funds
and high net-worth individuals.

@@

In this report I've given a brief overview my attempts to elute
maximal insight from a single large dataset through statistical
modelling, visualisations and other data science techniques. Together
these form a narrative of investigative analysis into a single
exemplar postcode, and the assessment of the potential investment
returns within.

>>>>

%----------------------------------------------------------------------------------------
%	ABSTRACT
% ----------------------------------------------------------------------------------------
\vspace{-4em}
\section*{Overview}

@@

I analysed the {\bf London house prices} dataset in several creative
ways. Firstly, the \emph{fractal context} of an area visualises how house
prices relate to those of neighbouring regions at different scales up
and down the postcode hierarchy. Secondly, I fit \emph{ARIMA models}
to forecast an area's price trend into the future, with an eye to
suggesting profitable investments. Finally, growth and other metrics
were combined into an \emph{investment grade} for a given postcode
area. Together this set of analyses forms the basis of \logo, a
startup aimed at \emph{democratising real estate investment}, offering
individuals and businesses quantitative property area insights to
enable data-driven investment decisions.

@@

Property letting and sales sites sometimes list a few recent sales for
a given area, but it's not currently possible to get an overview
of the price distribution within an area, or to frame local prices
within the context of other nearby sectors, district and postcode.

@@

This can be addressed with a clear and intuitive data
visualisation of price distributions in the postcode hierarchy --- what
I've called the fractal context of a postcode (Figure 1).

Any chosen area can be seen in the context of its surroundings, from
exact full postcodes to much wider areas, clearly showing how the pricing of
any given property relates to those nearby.  The example graphic for
postcode SW18 4HU (Figure 1) combines ranked violin density plots and
a geo-heatmap for a varied and informative view of a location's price
context.

@@

Property investors need a method of evaluating the potential investment
returns for a given property area. This can be achieved through time
series modelling with autoregressive integrated moving average (ARIMA)
models (Figure 2). For this application regularised models were fit
which allowed a $drift$ term to capture non-stationary trends
(i.e. allowing for price gains, losses or neither) as well as coefficients
reflecting periodicity or seasonal effects. Predicted investment
returns can then be optimised by selecting areas with
maximal growth projections.

\begin{figure}[h]
\centering
\vspace{.5em}
\includegraphics[width=.9\textwidth]{Figures/arima.png}
\vspace{-.5em}
\caption{ ARIMA model and forecast of median monthly house prices for the
  SW18 4 sector.}
\vspace{.75em}
\end{figure}

\vspace{-1.8em}
\subsection*{Investment grading}

Combining growth forecasts and with an additional measure of
variability allows an approximate investment grading of each sector,
relative to all others covered by this dataset (over 2,500
sectors). This intuitive output metric can help prioritise areas ripe
for property investment and combines the theoretical model projections
with an empirical measure of past stability.

@@

There are currently no mainstream property sales or rental sites that
attempt to provide any quantitative insights that contextualise a
property's list price. Some list recent nearby sales in plain text,
but the wealth of historical sales data available allows for much
richer displays (as demonstrated with the fractal context view,
Section A: Figure 1, and by the interactive data-driven map shown in
Figure 5), which offer valuable and practical insights to prospective
homebuyers.

@@

\logo \hspace{.1em} will release an initial product both as a {\bf web
  service} and associated {\bf mobiles and tablet applications}
(Figure 6). These
offer limited analysis and visualisation without any fee, with
collected user data and feedback helping to validate the business
model and further develop our software.

@@

Releasing these products aligns with our aims of democratising real
estate investment. Amateur property investors and prospective
landlords can use our products to make data-driven decisions, the
likes of which are already employed by analysts for large investment
funds.

A small data science team will gradually expand the range of analyses
offered, integrating novel public and privately-acquired datasets and
releasing them to a premium app offered under a subscription model,
aimed at private landlords, professional property developers and
property speculators as well as real estate investment trusts
(REITs). Significant revenue could be generated through tailored
partnerships with funds and high net-worth individuals, likely
developed from leads that use this service.

@@

In this report I've given a brief overview my attempts to elute
maximal insights from a single large dataset through statistical
modelling, visualisations and other data science techniques. Together
these form a narrative of investigative analysis into a single
exemplar postcode, culminating in the assessment of potential investment
returns for properties in this area.
